Nuclei Segmentation in Histopathology images using Deep Neural Networks

### 2016-11-08 Paper.tex
reducing

% Template for ISBI-2016 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[francais]{babel}
\usepackage{hyperref}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

@@

Many traditional techniques have been proposed for the segmentation of
nuclei in histopathology images, ranging from simple background
subtraction and color threshold techniques\cite{Yuan2012} to much more
sophisticated approaches, such as marked point
processes\cite{Kulikova2012}. Many of these methods have been recently
reviewed \cite{irshad2014methods}.

@@

Alternative methods 
have arisen from the achieving Convolutional neural networks 
\cite{lecun}, in particular strong incentive rose with the very impressive 
results that they achieved in the pascal voc challenge with 
\cite{ImageNet}. Recent advances in deep neural networks, and in 
particular in their optimization have made them become the state-of-the-
art model for object recognition.  Deep neural network have also been 
used for 
semantic segmentation, where \cite{long2015fcn} use "de-
convolution layers" and up-sampling in order to identify and precisely 
locate objects within a picture. Different architecture arising from 
different intuition are also possible and have been applied in this paper.

@@

\begin{figure}[htb]
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{RGB_1}}
%  \vspace{1.5cm}
  \centerline{Sample from patient 498959}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{GT_1}}
%  \vspace{1.5cm}
  \centerline{Associated ground truth}\medskip
\end{minipage}
%
%
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{RGB_2}}
%  \vspace{1.5cm}
  \centerline{Sample from patient 581910}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{GT_2}}
%  \vspace{1.5cm}
  \centerline{Associated ground truth}\medskip
\end{minipage}
%
%
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{RGB_3}}
%  \vspace{1.5cm}
  \centerline{Another one from patient 581910}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{GT_3}}
%  \vspace{1.5cm}
  \centerline{Associated ground truth}\medskip
\end{minipage}
%
\caption{Random annotated samples from the dataset}
\label{fig:annotation}
%
\end{figure}

@@

%% Contribution as a dataset, small introduction
\noindent One of the contributions of this paper is the now publicly available 
nuclei detection dataset within HE stained histopathology images which 
can be found at \url{http://cbio.mines-paristech.fr/~pnaylor/Downloads/HECellSegmentation.zip} 
(not a true address). This annotated dataset provides images clustered by 
patients. Each patient has at least 3 annotated $512 \times 512$ HE 
histopathology images with their associated ground truth. Each 
ground truth image is a $512 \times 512$ label image where each pixel value above 
$0$ is considered as the label of the corresponding nucleus. 
See figure \ref{fig:annotation} for an example of 
three annotated images. This annotation was conducted via the help of 
the software ITK-snap, \cite{py06nimg} \url{http://www.itksnap.org} by
the authors of this paper.

@@

\begin{figure}[htb]
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[height=4.0cm]{RGB_pred}}
%  \vspace{1.5cm}
  \centerline{Original RGB sample}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{GT_pred}}
%  \vspace{1.5cm}
  \centerline{Associated ground truth}\medskip
\end{minipage}

@@

%
%
\begin{minipage}[b]{0.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNetB}}
%  \vspace{1.5cm}
  \centerline{DeconvNet}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNetP}}
%  \vspace{1.5cm}
  \centerline{Probability map}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNet_WS}}
%  \vspace{1.5cm}
  \centerline{Watershed}\medskip
\end{minipage}
%
\begin{minipage}[b]{0.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCNB}}
%  \vspace{1.5cm}
  \centerline{FCN}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCNP}}
%  \vspace{1.5cm}
  \centerline{Probability map}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCN_WS}}
%  \vspace{1.5cm}
  \centerline{Watershed}\medskip
\end{minipage}
%
\caption{Prediction via different classifiers of a random sample on the left out patient: 581910}
\label{fig:prediction}
%
\end{figure}

@@

\section{Different architectures/Results}
\label{sec:results}
\noindent We experience with 3 known arhitectures in semantic segmentation, named PangNet, Fully Convolutionnal Net (FCN) and DeconvNet. The most basic architecture, PangNet, consists of 4 
convolutionnal layer where each convolutionnal layer has 8 feature map, for more information please refer to \cite{pang2010cell}. 
This net, being not deep, has the advantage of being less 
computationnally intensive. FCN is a first attempt of applying "deep 
feature" representations to the task of semantic segmentation. This 
architecture has the advantage of re-using a classical deep learning 
architecture with additional upsampling and skip layers. The 
upsampling layers enable the network to learn a pixel level classification 
and the skip layers enable the network to fuse different levels of 
abstraction to the final prediction. This model can be fine tuned with a 
set of pretrained-weights extracted from the classical deep learning 
architecture\cite{long2015fcn}. DeconvNet is also based on a classical architecture, 
however, in this network their are no skip layers as one intends to learn 
the proper upsampling through repeated deconvolution and convolution 
layers. This model can also be fine tuned\cite{noh2015learning}. We also did an
ensemble classifier of these two previous nets as suggested in 
\cite{noh2015learning}.
% The final architecture that we tried is the UNet. This network combines 
%both contribution of the above networks, the UNet has a similar 
%architecture to the DeconvNet with skip layers.
\section{Result and discussion}
\label{sec:result}
\noindent We conducted our experiments on GPUs via the caffe framework, 
\cite{jia2014caffe}. We present our results in table \ref{tab:res} where 
we averaged the metrics over all left out patients. We also added, for 
illustration purposes \ref{fig:prediction}, image predictions and 
associated 
probability maps to evaluate some differences between the classifiers. 
We notice that the simpler net, PangNet seems to have learnt simple 
rules such as color information. As soon as the nuclei are not
homogeneous and dark inside, the method fails ( "holes" in the
cells). On the 
contrary, deeper nets as FCN and DeconvNet have learnt deeper features 
and seem capable of recognizing whole cells. On these probability maps 
we applied our watershed segmentation and we can picture the results in 
the third 
column. By construction, our post-processing 
scheme is very sensitive to noise as we can see in the PangNet 
prediction, many unrelated minimas will lead to highly partitionned cell. 
This phenomenom also appears with the DeconvNet where undesired 
cuts were performed, like for the cell at the bottom left of the image. 
We picked $\lambda = 7$ which seemed to give a nice partitionning of 
the image, this value can be found by cross validation or by simple 
visualization of the results.
\begin{table}
\begin{tabular}{|c|c|c|c|c|}
\hline
  & PangNet & DeconvNet & FCN & Ensemble\\
 \hline
Accuracy  &       0.936 & 0.968 &0.958 & 0.968  \\
IU   &    0.759 &     0.856 & 0.857 & 0.861 \\
Recall     &       0.744  &     0.856 & 0.855 & 0.876\\
Precision   &       0.741 &     0.858 & 0.878 & 0.851\\
F1    &       0.742 &     0.856 & 0.866  & 0.863\\
TP       &       0.744 &     0.856 & 0.855 & 0.876 \\
TN      &       0.963 &     0.981 &  0.977 & 0.979\\
Performance    &       0.853 &     0.918 & 0.916 & 0.928\\
Pixel error  &  0.063 &     0.032 & 0.042 & 0.032\\
\hline
\end{tabular}
\caption{Results}
\label{tab:res}
\end{table}

@@

We presented a fully automized workflow for segmenting nuclei in
histopathology images based on deep learning and mathematical
morphology. We have also generated a manually curated segmentation
data base, which we make publicly available. We believe that such a
method can become very useful for the investigation of cellular
phenotypes at a tissue level and their relation to disease.

%I don't really know if we need something like this...

%%with Unet
%\begin{tabular}{|c|c|c|c|c|c|}
% & UNet & PangNet & DeconvNet & FCN & Ensemble \\
%\hrule
%Accuracy &       0.89 &       0.936 & 0.968 &0.958 & \\
%IU   &       0.70 &       0.759 &     0.856 & 0.857 &\\
%Recall    &       0.75 &       0.744  &     0.856 & 0.855 &\\
%Precision    &       0.64 &       0.741 &     0.858 & 0.878&\\
%F1       &       0.69 &       0.742 &     0.856 & 0.866&  \\
%TP             &       0.75 &       0.744 &     0.856 & 0.855 & \\
%TN             &       0.92 &       0.963 &     0.981 &  0.977&\\
%Performance    &       0.84 &       0.853 &     0.918 & 0.916&\\
%Pixel error  &       0.11 &       0.063 &     0.032 & 0.042&\\
%\end{tabular}

%\section{Formatting your paper}
%\label{sec:format}
%
%All printed material, including text, illustrations, and charts, must be kept
%within a print area of 7 inches (178 mm) wide by 9 inches (229 mm) high. Do
%not write or print anything outside the print area. The top margin must be 1
%inch (25 mm), except for the title page, and the left margin must be 0.75 inch
%(19 mm).  All {\it text} must be in a two-column format. Columns are to be 3.39
%inches (86 mm) wide, with a 0.24 inch (6 mm) space between them. Text must be
%fully justified.
%
%\section{PAGE TITLE SECTION}
%\label{sec:pagestyle}
%
%The paper title (on the first page) should begin 1.38 inches (35 mm) from the
%top edge of the page, centered, completely capitalized, and in Times 14-point,
%boldface type.  The authors' name(s) and affiliation(s) appear below the title
%in capital and lower case letters.  Papers with multiple authors and
%affiliations may require two or more lines for this information.
%
%\section{TYPE-STYLE AND FONTS}
%\label{sec:typestyle}
%
%To achieve the best rendering both in the proceedings and from the CD-ROM, we
%strongly encourage you to use Times-Roman font.  In addition, this will give
%the proceedings a more uniform look.  Use a font that is no smaller than nine
%point type throughout the paper, including figure captions.
%
%In nine point type font, capital letters are 2 mm high.  If you use the
%smallest point size, there should be no more than 3.2 lines/cm (8 lines/inch)
%vertically.  This is a minimum spacing; 2.75 lines/cm (7 lines/inch) will make
%the paper much more readable.  Larger type sizes require correspondingly larger
%vertical spacing.  Please do not double-space your paper.  True-Type 1 fonts
%are preferred.
%
%The first paragraph in each section should not be indented, but all the
%following paragraphs within the section should be indented as these paragraphs
%demonstrate.
%
%\section{MAJOR HEADINGS}
%\label{sec:majhead}
%
%Major headings, for example, "1. Introduction", should appear in all capital
%letters, bold face if possible, centered in the column, with one blank line
%before, and one blank line after. Use a period (".") after the heading number,
%not a colon.
%
%\subsection{Subheadings}
%\label{ssec:subhead}
%
%Subheadings should appear in lower case (initial word capitalized) in
%boldface.  They should start at the left margin on a separate line.
% 
%\subsubsection{Sub-subheadings}
%\label{sssec:subsubhead}
%
%Sub-subheadings, as in this paragraph, are discouraged. However, if you
%must use them, they should appear in lower case (initial word
%capitalized) and start at the left margin on a separate line, with paragraph
%text beginning on the following line.  They should be in italics.
%
%\section{PRINTING YOUR PAPER}
%\label{sec:print}
%
%Print your properly formatted text on high-quality, 8.5 x 11-inch white printer
%paper. A4 paper is also acceptable, but please leave the extra 0.5 inch (12 mm)
%empty at the BOTTOM of the page and follow the top and left margins as
%specified.  If the last page of your paper is only partially filled, arrange
%the columns so that they are evenly balanced if possible, rather than having
%one long column.
%
%In \LaTeX, to start a new column (but not a new page) and help balance the
%last-page column lengths, you can use the command ``$\backslash$pagebreak'' as
%demonstrated on this page (see the \LaTeX\ source below).
%
%\section{PAGE NUMBERING}
%\label{sec:page}
%
%Please do {\bf not} paginate your paper.  Page numbers, session numbers, and
%conference identification will be inserted when the paper is included in the
%proceedings.
%
%\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
%\label{sec:illust}
%
%Illustrations must appear within the designated margins.  They may span the two
%columns.  If possible, position illustrations at the top of columns, rather
%than in the middle or at the bottom.  Caption and number every illustration.
%All halftone illustrations must be clear black and white prints.  If you use
%color, make sure that the color figures are clear when printed on a black-only
%printer.
%
%Since there are many ways, often incompatible, of including images (e.g., with
%experimental results) in a \LaTeX\ document, below is an example of how to do
%this \cite{Lamp86}.

% Below is an example of how to insert images. Delete the ``\vspace'' line,
% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
% with a suitable PostScript file name.
% -------------------------------------------------------------------------

%\begin{minipage}[b]{0.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{BaochuanB}}
%%  \vspace{1.5cm}
%  \centerline{PangNet}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.5cm]{BaochuanP}}
%%  \vspace{1.5cm}
%  \centerline{Probability map}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{Baochuan_WS}}
%%  \vspace{1.5cm}
%  \centerline{Watershed}\medskip
%\end{minipage}
%
%%
%%
%\begin{minipage}[b]{0.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{DeconvNetB}}
%%  \vspace{1.5cm}
%  \centerline{DeconvNet}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{DeconvNetP}}
%%  \vspace{1.5cm}
%  \centerline{Probability map}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{DeconvNet_WS}}
%%  \vspace{1.5cm}
%  \centerline{Watershed}\medskip
%\end{minipage}
%%
%\begin{minipage}[b]{0.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{FCNB}}
%%  \vspace{1.5cm}
%  \centerline{FCN}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{FCNP}}
%%  \vspace{1.5cm}
%  \centerline{Probability map}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{FCN_WS}}
%%  \vspace{1.5cm}
%  \centerline{Watershed}\medskip
%\end{minipage}
%%
%\begin{minipage}[b]{0.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{EnsembleB}}
%%  \vspace{1.5cm}
%  \centerline{Ensemble}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{EnsembleP}}
%%  \vspace{1.5cm}
%  \centerline{Probability map}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{Ensemble_WS}}
%%  \vspace{1.5cm}
%  \centerline{Watershed}\medskip
%\end{minipage}
%\caption{Prediction via different classifiers of a random sample on the left out patient: 581910}
%\label{fig:prediction}
%%
%\end{figure}

% To start a new column (but not a new page) and help balance the last-page
% column length use \vfill\pagebreak.
% -------------------------------------------------------------------------
%\vfill
%\pagebreak

%\section{FOOTNOTES}
%\label{sec:foot}
%
%Use footnotes sparingly (or not at all!) and place them at the bottom of the
%column on the page on which they are referenced. Use Times 9-point type,
%single-spaced. To help your readers, avoid using footnotes altogether and
%include necessary peripheral observations in the text (within parentheses, if
%you prefer, as in this sentence).
%

%\section{COPYRIGHT FORMS}
%\label{sec:copyright}
%
%You must include your fully completed, signed IEEE copyright release form when
%you submit your paper. We {\bf must} have this form before your paper can be
%published in the proceedings.  The copyright form is available as a Word file,
%a PDF file, and an HTML file. You can also use the form sent with your author
%kit.

%\section{REFERENCES}
%\label{sec:ref}

%List and number all bibliographical references at the end of the
%paper.  The references can be numbered in alphabetic order or in
%order of appearance in the document.  When referring to them in the
%text, type the corresponding reference number in square brackets as
%shown at the end of this sentence \cite{C2}.

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{refs}

>>>>

% Template for ISBI-2016 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[francais]{babel}
%\usepackage{hyperref}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

@@

\noindent Many traditional techniques have been proposed for the segmentation of
nuclei in histopathology images, ranging from simple background
subtraction and color threshold techniques \cite{Yuan2012} 
to much more
sophisticated approaches, such as marked point
processes\cite{Kulikova2012}. Many of these methods have been recently
reviewed \cite{irshad2014methods}.

@@

Alternative methods 
have arisen from the achieving Convolutional neural networks 
%\cite{lecun}, 
%in particular strong incentive rose with the very impressive 
%results that they achieved in the pascal voc challenge with 
%\cite{ImageNet}. 
Recent advances in deep neural networks, and in 
particular in their optimization have made them become the state-of-the-
art model for object recognition.  Deep neural network have also been 
used for 
semantic segmentation, where \cite{long2015fcn} use "de-
convolution layers" and up-sampling in order to identify and precisely 
locate objects within a picture. Different architecture arising from 
different intuition are also possible and have been applied in this paper.

@@

\begin{figure}[htb]
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{RGB_1}}
%  \vspace{1.5cm}
  \centerline{Sample from patient 498959}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{GT_1}}
%  \vspace{1.5cm}
  \centerline{Associated ground truth}\medskip
\end{minipage}
%
%
%\begin{minipage}[b]{.48\linewidth}
 % \centering
%  \centerline{\includegraphics[width=4.0cm]{RGB_2}}
%  \vspace{1.5cm}
%  \centerline{Sample from patient 581910}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{0.48\linewidth}
%  \centering
%  \centerline{\includegraphics[width=4.0cm]{GT_2}}
%  \vspace{1.5cm}
%  \centerline{Associated ground truth}\medskip
%\end{minipage}
%
%
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{RGB_3}}
%  \vspace{1.5cm}
  \centerline{Another one from patient 581910}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{GT_3}}
%  \vspace{1.5cm}
  \centerline{Associated ground truth}\medskip
\end{minipage}
%
\caption{Random annotated samples from the dataset}
\label{fig:annotation}
%
\end{figure}

@@

%% Contribution as a dataset, small introduction
\noindent One of the contributions of this paper is the now publicly available 
nuclei detection dataset within HE stained histopathology images which 
can be found at \url{http://cbio.mines-paristech.fr/~pnaylor/BNS.zip} 
(not a true address). This annotated dataset provides images clustered by 
patients. Each patient has at least 3 annotated $512 \times 512$ HE 
histopathology images with their associated ground truth. Each 
ground truth image is a $512 \times 512$ label image where each pixel value above 
$0$ is considered as the label of the corresponding nucleus. 
See figure \ref{fig:annotation} for an example of 
three annotated images. This annotation was conducted via the help of 
the software ITK-snap, \cite{py06nimg} \url{http://www.itksnap.org} by
the authors of this paper.

@@

\begin{figure}[htb]
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[height=3.0cm]{RGB_pred}}
%  \vspace{1.5cm}
  \centerline{Original RGB sample}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=3.0cm]{GT_pred}}
%  \vspace{1.5cm}
  \centerline{Associated ground truth}\medskip
\end{minipage}

@@

%
%
\begin{minipage}[b]{0.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNetB}}
%  \vspace{1.5cm}
  \centerline{DeconvNet}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNetP}}
%  \vspace{1.5cm}
  \centerline{Probability map}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{DeconvNet_WS}}
%  \vspace{1.5cm}
  \centerline{Watershed}\medskip
\end{minipage}
%
\begin{minipage}[b]{0.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCNB}}
%  \vspace{1.5cm}
  \centerline{FCN}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCNP}}
%  \vspace{1.5cm}
  \centerline{Probability map}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{.32\linewidth}
  \centering
  \centerline{\includegraphics[height=2.4cm]{FCN_WS}}
%  \vspace{1.5cm}
  \centerline{Watershed}\medskip
\end{minipage}

%\begin{minipage}[b]{0.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{EnsembleB}}
%%  \vspace{1.5cm}
%  \centerline{Ensemble}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{EnsembleP}}
%%  \vspace{1.5cm}
%  \centerline{Probability map}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{.32\linewidth}
%  \centering
%  \centerline{\includegraphics[height=2.4cm]{Ensemble_WS}}
%%  \vspace{1.5cm}
%  \centerline{Watershed}\medskip
%\end{minipage}

%
\caption{Prediction via different classifiers of a random sample on the left out patient: 581910}
\label{fig:prediction}
%
\end{figure}

@@

\section{Different architectures}
\label{sec:results}
\noindent We experience with 3 known arhitectures in semantic segmentation, named PangNet, Fully Convolutionnal Net (FCN) and DeconvNet. The most basic architecture, PangNet, consists of 4 
convolutionnal layer where each convolutionnal layer has 8 feature map, for more information please refer to \cite{pang2010cell}. 
This net, being not deep, has the advantage of being less 
computationnally intensive. FCN is a first attempt of applying "deep 
feature" representations to the task of semantic segmentation. This 
architecture has the advantage of re-using a classical deep learning 
architecture with additional upsampling and skip layers. The 
upsampling layers enable the network to learn a pixel level classification 
and the skip layers enable the network to fuse different levels of 
abstraction to the final prediction. This model can be fine tuned with a 
set of pretrained-weights extracted from the classical deep learning 
architecture\cite{long2015fcn}. DeconvNet is also based on a classical architecture, 
however, in this network their are no skip layers as one intends to learn 
the proper upsampling through repeated deconvolution and convolution 
layers. This model can also be fine tuned\cite{noh2015learning}. We also did an
ensemble classifier of these two previous nets as suggested in 
\cite{noh2015learning} but did not include any illustration as the results of the FCN were better.

\section{Results and discussion}
\label{sec:result}
\noindent We conducted our experiments on GPUs via the caffe framework, 
\cite{jia2014caffe}. We present our results in table \ref{tab:res} where 
we averaged the metrics over all left out patients. We also added, for 
illustration purposes \ref{fig:prediction}, image predictions and 
associated 
probability maps to evaluate some differences between the classifiers. 
We notice that the simpler net, PangNet seems to have learnt simple 
rules such as color information. As soon as the nuclei are not
homogeneous and dark inside, the method fails ( "holes" in the
cells). On the 
contrary, deeper nets as FCN and DeconvNet have learnt deeper features 
and seem capable of recognizing whole cells. On these probability maps 
we applied our watershed segmentation and we can picture the results in 
the third 
column. By construction, our post-processing 
scheme is very sensitive to noise as we can see in the PangNet 
prediction, many unrelated minimas will lead to highly partitionned cell. 
This phenomenom also appears with the DeconvNet where undesired 
cuts were performed, like for the cell at the bottom left of the image. 
We picked $\lambda = 7$ which seemed to give a nice partitionning of 
the image, this value can be found by cross validation or by simple 
visualization of the results.
\begin{table}
\begin{tabular}{|c|c|c|c|c|}
\hline
  & PangNet & DeconvNet & FCN & Ensemble\\
 \hline
Accuracy  &       0.936 & 0.968 &0.958 & 0.968  \\
IU   &    0.759 &     0.856 & 0.857 & 0.861 \\
Recall     &       0.744  &     0.856 & 0.855 & 0.876\\
Precision   &       0.741 &     0.858 & 0.878 & 0.851\\
F1    &       0.742 &     0.856 & 0.866  & 0.863\\
% TP       &       0.744 &     0.856 & 0.855 & 0.876 \\
% TN      &       0.963 &     0.981 &  0.977 & 0.979\\
Performance    &       0.853 &     0.918 & 0.916 & 0.928\\
% Pixel error  &  0.063 &     0.032 & 0.042 & 0.032\\
\hline
\end{tabular}
\caption{Results}
\label{tab:res}
\end{table}

@@

\noindent We presented a fully automized workflow for segmenting nuclei in
histopathology images based on deep learning and mathematical
morphology. We have also generated a manually curated segmentation
data base, which we make publicly available. We believe that such a
method can become very useful for the investigation of cellular
phenotypes at a tissue level and their relation to disease.

%%with Unet
%\begin{tabular}{|c|c|c|c|c|c|}
% & UNet & PangNet & DeconvNet & FCN & Ensemble \\
%\hrule
%Accuracy &       0.89 &       0.936 & 0.968 &0.958 & \\
%IU   &       0.70 &       0.759 &     0.856 & 0.857 &\\
%Recall    &       0.75 &       0.744  &     0.856 & 0.855 &\\
%Precision    &       0.64 &       0.741 &     0.858 & 0.878&\\
%F1       &       0.69 &       0.742 &     0.856 & 0.866&  \\
%TP             &       0.75 &       0.744 &     0.856 & 0.855 & \\
%TN             &       0.92 &       0.963 &     0.981 &  0.977&\\
%Performance    &       0.84 &       0.853 &     0.918 & 0.916&\\
%Pixel error  &       0.11 &       0.063 &     0.032 & 0.042&\\
%\end{tabular}
\bibliographystyle{IEEEbib}
\bibliography{refs}
